---
title: "SARGE Data Visualization"
author: "Stephanie J. Wilson"
date: "2026-09-03"
output: pdf_document
---

THIS WILL BE A MARKDOWN EXPLAINING HOW TO VIZ SARGE DATA IF YOU WANT TO DO IT NOT ON THE DASHBOARD 

ALSO A STARTING POINT FOR SOME OF THE FUNCTIONS 

# Code to plot recent data collected by SARGE 

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(tidyverse)
library(lubridate)
library(plotly)
library(DT)

source("../SARGEtools_functions/sarge_read.R")
source("../SARGEtools_functions/sarge_plot.R")

TIMEZONE <- "EST"

```

# Set your SARGE configuration in order to plot data 

Need to set up a file that has links to your data files output by SARGE (these can be online in a Dropbox, Google Drive, Sharepoint, GitHub, etc). If you are not using an online repository, you can upload your files to a folder and put the path in the file_tab_descriptions.txt, but if you have an online repository you can put the link to the data. 

** ask Abby if we need a note about google drive authorization here 

Also set up a file that describes your variables. You can set the column names that your instrument or campbell code defines. 

```{r configure data, echo=FALSE}

# Define your files 
files <- read_delim(
  "../SARGE_configuredata/file_tab_descriptions.txt",
  show_col_types = FALSE, delim = "\t"
)

# Define your instrumentation, variables, and plotting colors 
variables <- read_csv(
  "../SARGE_configuredata/colname_descriptions.csv",
  show_col_types = FALSE
) %>%
  mutate(
    default = as.logical(default)
  ) %>%
  mutate(colname = if_else(is.na(colname), label, colname),
         label = if_else(is.na(label), colname, label))

# Define the date window you want to plot 
start_date = "2026-09-02"
end_date = "2026-09-03"

```




## Read in your SARGE Data

If you follow the data structures in the outline campbell code for the instrumentation: 


```{r cars}

data <- sarge_read(
  files = files,
  variables = variables,
  timezone = TIMEZONE,
  resolution = "minute"
)

```

# Plot data from SARGE using the sarge_plot function 

** Abby we may need to make a different function for the markdown rather than the shiny to make it a little more intuitive, because we are not 

```{r plot data, echo=FALSE}



# Plot the greenhouse gas data 
ghg <- plot_sarge(
  data = data,
  data_type = "GHG",
  start = start_date,
  end = as.Date("2026-09-03"),
  variables = variables
)

ghg










```






















