---
title: "SARGE Data Visualization"
author: "Stephanie J. Wilson"
date: "2026-09-03"
output: pdf_document
---

THIS WILL BE A MARKDOWN EXPLAINING HOW TO VIZ SARGE DATA IF YOU WANT TO DO IT NOT ON THE DASHBOARD 

ALSO A STARTING POINT FOR SOME OF THE FUNCTIONS 

# Code to plot recent data collected by SARGE 

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(tidyverse)
library(lubridate)
library(plotly)
library(DT)

source("../SARGEtools_functions/sarge_read.R")
source("../SARGEtools_functions/plot_sarge.R")

TIMEZONE <- "EST"

```

# Set your SARGE configuration in order to plot data 

Need to set up a file that has links to your data files output by SARGE (these can be online in a Dropbox, Google Drive, Sharepoint, GitHub, etc). If you are not using an online repository, you can upload your files to a folder and put the path in the file_tab_descriptions.txt, but if you have an online repository you can put the link to the data. 

If you are using google sheets, make the sheet so anyone with the link can view the file, then add this line to your code (install the googlesheets package first if you do not have it):
`googlesheets4::gs4_deauth()`

Also set up a file that describes your variables. You can set the column names that your instrument or campbell code defines. 

```{r configure data, echo=FALSE}

# Define your files 
files <- read_delim(
  "../SARGE_configuredata/file_tab_descriptions.txt",
  show_col_types = FALSE, delim = "\t"
)

# Define your instrumentation, variables, and plotting colors 
variables <- read_csv(
  "../SARGE_configuredata/colname_descriptions.csv",
  show_col_types = FALSE
) %>%
  mutate(
    default = as.logical(default)
  ) %>%
  mutate(colname = if_else(is.na(colname), label, colname),
         label = if_else(is.na(label), colname, label))

# Define the date window you want to plot 
start_date = "2026-09-02"
end_date = "2026-09-03"

```




## Read in your SARGE Data

If you follow the data structures in the outline campbell code for the instrumentation: 


```{r cars}

data <- sarge_read(
  files = files,
  variables = variables,
  timezone = TIMEZONE,
  resolution = "minute"
)

```

# Plot data from SARGE using the sarge_plot function 



```{r plot data, echo=FALSE}
data_type = "GHG"

# Get data for selected data type
ghg_data <- data[[data_type]]
  
# Get default variables and colors
var_info <- variables %>%
  filter(
    data_type == !!data_type,
    default == TRUE
  )

vars <- var_info$colname

colors <- setNames(
  var_info$color,
  var_info$colname
)

# Plot the greenhouse gas data 
ghg <- plot_sarge(
  data = ghg_data,
  start = start_date,
  end = end_date,
  vars = var_info$colname,
  colors = colors
)

ghg

```



