---
title: "SARGE Data Visualization"
author: "Stephanie J. Wilson"
date: "2026-09-03"
output: pdf_document
---

# Code to visualize current data collected by SARGE 

## Set up code 
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(tidyverse)
library(lubridate)
library(plotly)
library(DT)
library(SARGEtools)

TIMEZONE <- "EST"

```

## Define files and variables  

```{r configure data, echo=FALSE}

# Define your files 
files <- read_delim(
  "../SARGE_configuredata/file_descriptions.txt",
  show_col_types = FALSE, delim = "\t"
)

# Define your instrumentation, variables, and plotting colors 
variables <- read_csv(
  "../SARGE_configuredata/variable_descriptions.csv",
  show_col_types = FALSE
) %>%
  mutate(
    default = as.logical(default)
  ) %>%
  mutate(colname = if_else(is.na(colname), label, colname),
         label = if_else(is.na(label), colname, label))

# Define the date window you want to plot 
start_date = "2026-01-17"
end_date = "2026-01-19"

```




## Read in your SARGE Data with sarge_read()

```{r cars}

data <- sarge_read(
  files = files,
  variables = variables,
  timezone = TIMEZONE,
  resolution = "minute"
)

head(data)

```

# Plot data from SARGE using the sarge_plot_defaults() function 

## Physiochemical Data: Measurements made by the Xylem EXO2 Sonde in the example data 

```{r plot physiochemical data, warning=FALSE}

# Set the desired data_type from your data (must match a data_type in variables)
data_type = "Physiochemistry"

# Plot the greenhouse gas data from SARGE 
exo_plot <- sarge_plot_defaults(
                    data = data,               
                    data_type = data_type,    
                    start = start_date,       
                    end = end_date,           
                    variables = variables)    

# Print the Plot 
exo_plot 


```    

## Hydrologic Data: Measurements made by the Sontek IQ ADCP in the example data 

```{r plot ADCP data, warning=FALSE}

# Set the desired data_type from your data (must match a data_type in variables)
data_type = "Hydrology"

# Plot the greenhouse gas data from SARGE 
adcp_plot <- sarge_plot_defaults(
                    data = data,              
                    data_type = data_type,    
                    start = start_date,       
                    end = end_date,           
                    variables = variables)    

# Print the Plot 
adcp_plot 


```    

## Greenhouse Gas Data: Measurements made by a LICOR 7810 in the example data 

```{r plot GHG data, warning=FALSE}

# Set the desired data_type from your data (must match a data_type in variables)
data_type = "GHG"

# Plot the greenhouse gas data from SARGE 
ghg_plot <- sarge_plot_defaults(
                    data = data,              
                    data_type = data_type,    
                    start = start_date,       
                    end = end_date,           
                    variables = variables)    

# Print the Plot 
ghg_plot 


```    

## Radon Gas Data: Measurements made by a Durridge RAD7 in the example data 

```{r plot Radon data, warning=FALSE}


# Set the desired data_type from your data (must match a data_type in variables)
data_type = "Radon"

# Plot the greenhouse gas data from SARGE 
rad7_plot <- sarge_plot_defaults(
                    data = data,              
                    data_type = data_type,    
                    start = start_date,       
                    end = end_date,           
                    variables = variables)    

# Print the Plot 
rad7_plot 




```   

