---
title: "SARGE Real Time Data Visualization Code"
author: "Stephanie J. Wilson"
date: Sys.Date()
output: pdf_document
---


```{r setup, include=FALSE}

# Load necessary packages 
library(data.table); library(tidyverse)
library(readxl); library(lubridate)
library(ggpubr); library(cowplot)
library(plotrix)

# 

```

## Would be nice to have a table that is output that has the logger power in and out
#then to plot those data to look for battery level loss. 

## EXO2 Sonde (Xylem Analytics) Current Data 
```{r, echo=FALSE}

#Read in current water quality sonde (EXO2) data from SARGE
exo <- read.table("Data/WILSON_ExoTable.dat", header=TRUE, skip=3, sep= ",")

#Take a quick look at the data 
head(exo)

#could consider putting these into a csv that then I read in for the EXO to be cleaner... 
colnames(exo) <- c("TIMESTAMP","RECORD","Date","Time","Chlorophyll_RFU","Chlorophyll_ugL",
              "Conductivity","FDOM_QSU","FDOM_RFU","NLF_conductivity",
              "ODO_sat","ODO_local", "ODO_MgL", "Pressure_psia", "Salinity_PPT", 
              "Specific_Conductivity_uScm", "BGA_PE_RFU", "BGA_PE_ugL",
              "TDS_mg_L","Turbidity_FNU","Wiper_Position_mv","pH","pH_mv","Temp_C", 
              "Depth_m","Battery_v","Cable_v","Wiper_Current_ma","sn","snn")


#Make a new timestamp column that is recognized as date + time measured in the timezone needed:
exo$TIMESTAMP <- ymd_hms(exo$TIMESTAMP, tz = "EST")

exo <- exo %>%
  filter(TIMESTAMP > "2026-09-01")

#Ensure that columns that should be numbers are numeric for plotting:
exo$Depth_m <- as.numeric(exo$Depth_m)
exo$Conductivity <- as.numeric(exo$Conductivity)


## Plot Waterlevel (Depth_m)
waterlev <- ggplot(exo, aes(x=TIMESTAMP, y=Depth_m)) + geom_point(color="blue") + ylim(-0.5,2.5) #+ xlim(c(as.POSIXct('2024-09-19 00:00:00', format = "%Y-%m-%d %H:%M:%S"),
     #as.POSIXct('2024-09-28 00:00:00', format = "%Y-%m-%d %H:%M:%S"))) + theme_classic()
waterlev

## Plot conductivity 
cond <- ggplot(exo, aes(x=TIMESTAMP, y=Salinity_PPT)) + geom_point(color="purple") #+ 
  #xlim(c(as.POSIXct('2024-09-19 00:00:00', format = "%Y-%m-%d %H:%M:%S"),
     #as.POSIXct('2024-09-28 00:00:00', format = "%Y-%m-%d %H:%M:%S"))) + theme_classic()
cond

## Can plot as many or as few variables as needed, consider plotting what is useful for checks

```

## SontekIQ series (Xylem Analytics) Current Data 
```{r, echo=FALSE}

#read in hydrologic data from Sontek IQ (Xylem Analytics)
sontek <- read.table("Data/WILSON_SontekTable.dat", header=TRUE, skip=1, sep= ",")
sontek <- sontek[-(1:3), ]
sontek <- as.tibble(sontek)

#Take a quick look at the tibble created
head(sontek)

#Make a new timestamp column that is recognized as date + time measured in the timezone needed:
sontek$TIMESTAMP <- ymd_hms(sontek$TIMESTAMP, tz = "EST")

sontek <- sontek %>%
  filter(TIMESTAMP > "2026-09-01")

#Ensure that columns that should be numbers are numeric for plotting:
sontek$Flowrate <- as.numeric(sontek$Flowrate)
sontek$Water_depth <- as.numeric(sontek$Water_depth)
sontek$Index_velocity <- as.numeric(sontek$Index_velocity)

## Plot Sontek Flow Data: 
flow <- ggplot(sontek, aes(x=TIMESTAMP, y=Flowrate)) + geom_point(color="black") +       
  #xlim(c(as.POSIXct('2024-09-19 00:00:00', format = "%Y-%m-%d %H:%M:%S"),
    # as.POSIXct('2024-09-28 00:00:00', format = "%Y-%m-%d %H:%M:%S"))) + 
      theme_classic()
flow

## Plot Index Velocity or Water flow Velocity 
flow1 <- ggplot(sontek, aes(x=TIMESTAMP, y=Index_velocity)) + geom_point(color="black") + theme_classic()       
  #xlim(c(as.POSIXct('2024-09-19 00:00:00', format = "%Y-%m-%d %H:%M:%S"),
     #as.POSIXct('2024-09-28 00:00:00', format = "%Y-%m-%d %H:%M:%S"))) 
flow1

## Plot water depth measured by the sontekIQ 
sdepth <- ggplot(sontek, aes(x=TIMESTAMP, y=Water_depth)) + geom_point(color="darkblue") + theme_classic()
    #xlim(c(as.POSIXct('2024-09-19 00:00:00', format = "%Y-%m-%d %H:%M:%S"),
     #as.POSIXct('2024-09-28 00:00:00', format = "%Y-%m-%d %H:%M:%S"))) 
sdepth


```

## LI7810 CH4/CO2/H2O Trace Gas Analyzer (LI-COR) Data from lab test when I simulated increasing CO2 concentrations then shut off the pump 
```{r, echo=FALSE}
#Note that similar code could be used with a LI7820 N2O Analyzer 

#read in gas concentration data from the LI7810 (LI-COR)
flux <- read.table("Data/WILSON_FLUX_7810.dat", header=TRUE, skip=1, sep= ",")
flux <- flux[-(1:2), ]

#Take a quick look at the dataframe created
head(flux)

#Make a new timestamp column that is recognized as date + time measured in the timezone needed:
flux$TIMESTAMP1 <- ymd_hms(flux$TIMESTAMP, tz = "EST")

flux <- flux %>%
  filter(TIMESTAMP > "2026-09-01")

#Ensure that columns that should be numbers are numeric for plotting:
flux$CH4d_ppm <- as.numeric(flux$CH4)
flux$CO2d_ppm <- as.numeric(flux$CO2)


## Plot CH4 Data (Note: these are raw concentrations, not in water concentrations)
ghg_CH4 <- ggplot(flux, aes(x=TIMESTAMP1, y=CH4d_ppm)) + geom_point(color="darkviolet")+
  xlim(c(as.POSIXct('2026-09-04 10:46:15', format = "%Y-%m-%d %H:%M:%S"),
    as.POSIXct('2026-09-04 12:00:00', format = "%Y-%m-%d %H:%M:%S"))) +
  
  scale_y_continuous( limits = c(2000, 2200), breaks = seq(2000, 2200, 50)) + 
  
  labs(x = " ", y = expression("CH"[4]~ "(ppb)")) +
  
  theme_bw() +
  
  geom_hline(
    yintercept = 2050, linetype = "dashed",color = "black", linewidth = 0.8) +

  theme(
    axis.text.x = element_text(angle = 0, size = 14 ),
    axis.title.y = element_text(size = 14),
    axis.text.y = element_text(size = 14),
    #strip.text = element_text( size = 14),
    legend.position = "none")
    
ghg_CH4

## Plot CO2 Data (Note: these are raw concentrations, not in water concentrations)
ghg_CO2 <- ggplot(flux, aes(x=TIMESTAMP1, y=CO2d_ppm)) + geom_point(color="navy") + 
  xlim(c(as.POSIXct('2026-09-04 10:46:15', format = "%Y-%m-%d %H:%M:%S"),
    as.POSIXct('2026-09-04 12:00:00', format = "%Y-%m-%d %H:%M:%S"))) +
  
  scale_y_continuous( limits = c(0, 3100), breaks = seq(0, 3000, 500)) + 
  
  labs(x = " ", y = expression("CO"[2]~ "(ppm)")) +
  
  theme_bw() +
  
  geom_hline(
    yintercept = 475, linetype = "dashed",color = "black", linewidth = 0.8) +

  theme(
    axis.text.x = element_text(angle = 0, size = 14 ),
    axis.title.y = element_text(size = 14),
    axis.text.y = element_text(size = 14),
    #strip.text = element_text( size = 14),
    legend.position = "none")
ghg_CO2


pump_off_fig1 <- plot_grid(ghg_CH4, ghg_CO2, ncol = 2) #, align = "v", vjust = 1)
pump_off_fig1


```


# Let's also look at the LICOR data from SWH and see if we can see when the pump shut off when the power went off 
```{r}

library(fluxfinder)

data <- ffi_read_LI7810("Data/TG10-01087-2024-08-09T120000.dat")



ggplot(data, aes(x=TIMESTAMP, y=CO2)) + geom_point() + 
    xlim(c(as.POSIXct('2024-08-19 00:00:00', format = "%Y-%m-%d %H:%M:%S"),
    as.POSIXct('2024-08-19 12:00:00', format = "%Y-%m-%d %H:%M:%S"))) + 
    scale_y_continuous( limits = c(0, 7500)) #, breaks = seq(0, 3000, 500)) 

ggplot(data, aes(x=TIMESTAMP, y=CH4)) + geom_point() + 
    xlim(c(as.POSIXct('2024-08-19 00:00:00', format = "%Y-%m-%d %H:%M:%S"),
    as.POSIXct('2024-08-19 12:00:00', format = "%Y-%m-%d %H:%M:%S"))) + 
    scale_y_continuous( limits = c(0, 300000)) #, breaks = seq(0, 3000, 500)) 
  

```






